Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
Remove appendix
Nits

To answer this question, this paper presents \sys, a shell \todo{preprocessor} that transforms shell pipelines into their distributed equivalents, enabling \emph{distribution-oblivious programming}.
The key insight behind \sys is that a large part of the shell language can be encoded using a dataflow graph model, providing structure to distribute computations.
%% \kk{Replaced that: the language of the Unix shell already encodes stream processing, providing most of the information required to distribute a computation. }
% FIXME \kk{I am not sure whether stream processing provides information for distributing a computation on its own. Maybe we can say that the shell exposes operator level parallelism, and that this is the first step to distributing a computation}.
\sys builds on this insight with a careful study of the distributability properties of shell primitives and commands, a definition of a dataflow graph model that is suitable for the shell, a set of parallelization optimizations that preserve the behaviour of the graph, and a late-bound command-prefixing scheme for deferring scheduling decisions to the distributed planner (\ie when runtime information is available).
A \sys-enabled $p_1$ will run \ttt{tr}s in parallel streams,
  use a mostly-parallel tree of \ttt{sort}s,
  run \ttt{uniq} mostly in parallel,
  \ttt{head} in one of the streams,
  and (trivially) merge streams in \ttt{out}.

@@

The paper is structured as follows.  It first starts with a background
section outlining pipeline concepts and overviewing \sys~\sx{bg}.
Sections \ref{distributability}--\ref{recipes} highlight key
contributions: \TODO{Change the 1st and the 3rd to reflect the new
  section layout. I already changed the second.}
\begin{itemize}

@@

This section presents (i) important background on shell pipeline composition~\sx{bg:pipelines}, and (ii)) a high-level overview of \sys's design and implementation.

@@

Before describing the different types of parallelization
optimizations, we formalize the intuition about stateless and pure
commands that was described in \Cref{cmd}.
\nv{TODOs
  (i) highlight earlier the antithesis between the formalisms in this section and the informalities of the previous (me)
}
%
As mentioned there, stateless commands operate independently on
individual elements of the stream (characters, lines, or files)
without maintaining any state. Some examples include \ttt{grep},
\ttt{basename}, and \ttt{tr}. Formally, a commmand $f$ is stateless if
it is ``linear'' with respect to concatenation, i.e. the following
equation holds:

@@

%% Appendix
\appendix
\section{Scripts used in the evaluation}

This appendix contains the source code of the scripts used in the evaluation of
the \sys. They are part of the codebase (released as open source with the camera
ready), and are provided here only to aid the reviewers.

>>>>

To answer this question, this paper presents \sys, a shell variant that transforms traditional shell pipelines into their distributed equivalents, enabling \emph{distribution-oblivious programming}.
The key insight behind \sys is that a large part of the shell language can be encoded using a dataflow graph model, providing structure to distribute computations.
%% \kk{Replaced that: the language of the Unix shell already encodes stream processing, providing most of the information required to distribute a computation. }
% FIXME \kk{I am not sure whether stream processing provides information for distributing a computation on its own. Maybe we can say that the shell exposes operator level parallelism, and that this is the first step to distributing a computation}.
\sys builds on this insight with a careful study of the distributability properties of shell primitives and commands, a definition of a dataflow graph model that is suitable for the shell, a set of parallelization optimizations that preserve the behaviour of the graph, and a late-bound command-prefixing scheme for deferring scheduling decisions to the distributed planner (\ie when runtime information is available).
A \sys-enabled $p_1$ will run \ttt{tr}s in parallel streams,
  use a mostly-parallel tree of \ttt{sort}s,
  run \ttt{uniq} mostly in parallel,
  \ttt{head} in one of the streams,
  and (trivially) merge streams in \ttt{out}.

@@

The paper is structured as follows.  It first starts with a background
section outlining pipeline concepts and overviewing \sys~\sx{bg}.
Sections \ref{distributability}--\ref{impl} highlight key
contributions:
\begin{itemize}

@@

This section presents (i) important background on shell pipeline composition~\sx{bg:pipelines}, and (ii) a high-level overview of \sys's design and implementation.

@@

Before describing the different types of parallelization
optimizations, we formalize the intuition about stateless and pure
commands that was described in \Cref{cmd}.
%% \nv{TODOs
%%   (i) highlight earlier the antithesis between the formalisms in this section and the informalities of the previous (me)
%% }
%
As mentioned there, stateless commands operate independently on
individual elements of the stream (characters, lines, or files)
without maintaining any state. Some examples include \ttt{grep},
\ttt{basename}, and \ttt{tr}. Formally, a commmand $f$ is stateless if
it is ``linear'' with respect to concatenation, i.e. the following
equation holds:

@@

%% %% Appendix
%% \appendix
%% \section{Scripts used in the evaluation}

%% This appendix contains the source code of the scripts used in the evaluation of
%% the \sys. They are part of the codebase (released as open source with the camera
%% ready), and are provided here only to aid the reviewers.
